From Education to Entrepreneurship

### 2014-12-11 index.Rmd
Revised website with simple charts

>>>>

We have included our findings in a detailed paper available here.  In sum, however, the most statistically significant and important findings from our analysis are that there is some evidence of a postitive relationship between higher levels of self-confidence reinforcement in teaching (a higher "WayofTeaching" score) and the rate of people owning their own business.  This can be seen in the chart below.  As we can see, however, when we add a trendline for each country the relationship becomes less certain.  For example, in the case of the United States and the United Kingdom, the country-specific trend line has a decreasing slope.  We believe this may be due to inconsistency in the survey and that a larger data set would allow us to more accurately describe the relationship between these variables.

```{r echo = FALSE, cache= FALSE, include= TRUE}

CD_subset2 <- subset(CD_copy, iso2c %in% myvars2)

# Remove unecessary columns
CD_subset$X <- NULL
CD_subset$iso2c <- NULL
CD_subset$PercentFear <- NULL
CD_subset$PercentNascent <- NULL
CD_subset$PercentPerceived <- NULL
CD_subset$PercentIntention <- NULL
CD_subset$PercentOpportunities <- NULL

# Create plot of WoT and PercentOwner
CD_subset %>% 
  ggvis(~WayofTeaching, ~PercentOwner) %>% 
  layer_points(fill = ~factor(Country)) %>%
  group_by(Country) %>%
  layer_model_predictions(model = "lm")
```

In addiiton, we can see a positive relationship between the percentage of respondents who believe there are opportunities to establish their own business (the percentage of people perceiving opportunities) and the rate of business ownership as reported in the survey.  This relationship can be seen in the following chart.  Similar to our findings above, this chart seems to show an overall positive relationship, but looking at country-specific factors, we can see that data from Japan indicates a negative slope.  We believe access to additional data would allow us to more accurately describe the relationship between these variables and then to investigate why these differences exist.

```{r echo = FALSE, cache= FALSE, include= TRUE}

# Drop unnecesssary columns in copied df
CD_subset2$X <- NULL
CD_subset2$iso2c <- NULL
CD_subset2$PercentFear <- NULL
CD_subset2$PercentNascent <- NULL
CD_subset2$PercentPerceived <- NULL
CD_subset2$PercentIntention <- NULL
CD_subset2$WayofTeaching <- NULL

# Create plot of PercentOpp and PercentOwner
CD_subset2 %>% 
  ggvis(~PercentOpportunities, ~PercentOwner) %>% 
  layer_points(fill = ~factor(Country)) %>%
  group_by(Country) %>%
  layer_model_predictions(model = "lm")

(Take this for the paper)
